\titleNameLong{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
updated acknowledgements

% Acknowledgments
\begin{acks}
TODO The author would like to thank Dr. Penry for teaching this course and
providing extensive design and learning opportunities.
\end{acks}

>>>>

% Acknowledgments
\begin{acks}
The author would like to thank Dr. Penry for teaching this course and for
providing extensive design and learning opportunities in this course. It has
been a lot of work, but this course has helped the author know that he has
chosen the right field.
\end{acks}
